Supplementary Materials for Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-07-02 analysis/supplementary materials/Supplementary Materials.Rmd
Use bookdown rather than officedown for Word out

---
title: "Supplementary Materials for Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson M. Del Ponte:
      institute: UFV
  - Kaique S. Alves:
      institute: UFV
  - Zachary S. L. Foster:
      institute: OSU
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
output: 
  officedown::rdocx_document:
     pandoc_args:
       - '--lua-filter=pagebreak.lua'
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/phytopath_template.docx"
---

>>>>

---
title: "Supplementary Materials for Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson M. Del Ponte:
      institute: UFV
  - Kaique S. Alves:
      institute: UFV
  - Zachary S. L. Foster:
      institute: OSU
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
output: 
  bookdown::word_document2:
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/phytopath_template.docx"
     pandoc_args:
       - '--lua-filter=scholarly-metadata.lua'
       - '--lua-filter=author-info-blocks.lua'
       - '--lua-filter=pagebreak.lua'
---
